---
title: "HW5"
author: "Seonyoung Park (sp3804)"
date: "11/10/2020"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(rvest)
library(purrr)
library(labelled)
```

```{r}
homicide_df = read.csv("homicide-data.csv")

```

```{r}

homicide_df = homicide_df %>%
  mutate(
    city_state=str_c(city,state, sep="_"),
    resolved=case_when(
      disposition=="Closed without arrest"~"unsolved",
      disposition=="Open/No arrest"~"unsolved",
      disposition=="Closed by arrest"~"solved",
    )
  )

```



```{r}
aggregate_df = 
  homicide_df %>%
  group_by(city_state) %>%
  summarise(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )

```


Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>%filter(city_state == "Baltimore_MD") %>%pull(hom_unsolved),
  aggregate_df %>% filter(city_state=="Baltimore_MD")%>% pull(hom_total)) %>%
    broom::tidy()


```

Try to iterate...


aggregate_df %>%
  mutate(
    prop_tests=map2(.x=hom_unsolved, .y=hom_total, ~prop.test(x=.x, n=.y)),
    tidy_tests=map(.x=prop_tests, ~broom::tidy(.x))
  ) %>%
  select(-prop_tests) %>%
  unnest(tidy_tests) %>%
  select(city_state, estimate, conf.low, conf.high)



## Problem 2 ideas....
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}

path_df = 
  tibble(
    path = list.files("lda_data")
  ) %>%
  mutate(path = str_c("lda_data/", path)
         )


read = function(x) {
  read_csv(x)
}

path_df = path_df %>%
  mutate(data = map(.x=path_df$path, ~read(.x))) 


data = unnest(path_df,data) %>%
   separate(path, c("file", "data","arm", "ID"),
                       extra='drop') %>%
    select(-"file",-"data") 

data
data%>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "value"
  )%>%
  ggplot(aes(x=week, y=value, group=ID, color=ID))+ geom_line() +facet_wrap("arm")
````

Based on the spaghetti plot above, case and control group show different trend.


